Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-16 Manuscript/ms.tex
update section4
update 语法

\title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
\author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Yihua Huang\corref{correspondingauthor}}
\cortext[correspondingauthor]{Corresponding author}
\ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, yhuang\}@nju.edu.cn}
\address{State Key Laboratory for Novel Software Technology, Department of Computer Science and Technology, Nanjing University, Nanjing 210023, China}

\begin{abstract}
    Graph neural network has become a research hotspot in the field of artificial intelligence due to the high accuracy results 
    obtained in many grpah-related task. At the same time, various of graph neural network system has emrged one after another.
    These systems have used their own skills in implementation, but there is very few work to discuss the performance bottleneck
    on graph neural network. In contrast to prior works that presents characterization of GCNs and selcts GNNs cover GNN workloads,
    we select typical algorithm by complexity of vertex/edge calculation. We analyze the performance bottleneck by breaking down training
    time, study the affects of hyper-parameters and sampling technology and find factors of memory usage. We finally put forwrd some key
    findings for GNN training and hope our work can help GNN system researchers. 
\end{abstract}

@@

\section*{Acknowledgment}

>>>>

\title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
\author{Zhaokang Wang, Yunpan Wang}
\cortext[correspondingauthor]{Corresponding author}
\ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, yhuang\}@nju.edu.cn}
\address{State Key Laboratory for Novel Software Technology, Department of Computer Science and Technology, Nanjing University, Nanjing 210023, China}

\begin{abstract}
    Graph neural network has become a research hotspot in the field of artificial intelligence due to the high accuracy results 
    obtained in many grpah-related tasks. At the same time, various of graph neural network system has emrged one after another.
    These systems have used their own skills in implementation, but there are very few works to discuss the performance bottleneck
    on graph neural network training. In contrast to prior works that present characterization of GCNs and select GNNs cover GNN workloads,
    we select typical algorithm by complexity of vertex/edge calculation. We analyze the performance bottleneck by breaking down training
    time, study the affects of hyper-parameters and sampling technology and find factors of memory usage. We finally put forwrd some key
    findings for GNN training and hope our work can help GNN system researchers. 
\end{abstract}

@@
